---
format: 
  revealjs:
    slide-number: true
    theme: [default, custom_theme.scss]
    preview-links: auto
    output-file: "index"
    output-ext: "html"
    output-dir: "../docs"
    logo: "Materials/About/personal_sticker.png"
    include-in-header: "fonts-include.html"
    highlight-style: github-light
    code-line-numbers: false
    code-overflow: scroll
    code-link: false
    embed-resources: true
    center-title-slide: false
---

```{r}
#| label: setup
#| include: false
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.align = "center",
  out.width = "100%",
  dpi = 300,
  fig.align = "center"
)

if (!require("here")) install.packages("here")
library(here)
here::i_am("Presentation/presentation.qmd")

if (!require("renv")) install.packages("renv")
library(renv)
renv::restore(
  lockfile = here::here("renv.lock"),
  prompt = FALSE
)

if (!require("countdown")) install.packages("countdown")
library(countdown)


if (!require("jsonlite")) install.packages("jsonlite")
library(jsonlite)

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

if (!require("qrcode")) install.packages("qrcode")
library(qrcode)

if (!require("cropcircles")) install.packages("cropcircles")
library(cropcircles)

include_local_figure <- function(data_source) {
  knitr::include_graphics(
    path = here::here(
      "Presentation",
      "Materials",
      data_source
    ),
    error = TRUE
  )
}

source(
  here::here(
    "R/set_r_theme.R"
  )
)
```


# Estimating Vegetation Change from Fossil Pollen to Planetary Boundaries :A Global, Long-Term Synthesis Using Big Data

## {.bg-black}

:::: {.columns}

::: {.column width="50%"}

<br>
<br>

```{r}
#| label: earth image
include_local_figure("AI_generated/Earth.jpeg")
```

:::

::: {.column width="50%" .text-center .center-vertical}

7/8 [global]{.text-highlight-purple} Earth system [boundaries]{.text-highlight-pink} are already [exceeded]{.text-highlight-orange} 

::: {.text-smaller .text-color-grey}
(Rockström et al. (2023))
:::

:::

::::

::: {.footer}
Image generated by Bing
:::

## {background-image="../Presentation/Materials/Pexels/pexels-justus-menke-3490295-5214145.jpg" background-opacity="0.65" .text-center}

:::: {.columns}

::: {.column width="25%"}
:::

::: {.column width="50%"} 

::: {.r-fit-text .text-bold .text-color-black .text-underline}
18%
:::

:::

::: {.column width="25%"}
:::

::::

::: {.blockquote}
Species to be exposed to [dangerous temperature]{.text-bold} condition  

::: {.text-smaller .text-color-grey}
([IPCC AR6 Synthesis Report](https://www.ipcc.ch/report/ar6/syr/downloads/report/IPCC_AR6_SYR_SPM.pdf))
:::

:::

::: {.footer}
Image by Justus Menke from Pexels
:::

## 🙋[Hi!]{.text-highlight-purple} I am [Ondřej Mottl]{.text-highlight-orange}

<br>

:::: {.columns}

::: {.column width="30%"}

```{r}
#| label: personal sticker
include_local_figure("About/head_photo.png")
```


:::


::: {.column width="70%"}

Assistant Professor at [Charles University](https://cuni.cz/UK-1.html), Prague, 🇨🇿

Head of the 🧑‍💻 [Laboratory of Quantitative Ecology](https://ondrejmottl.github.io/lab/about_the_lab.html)

:::

::::

:::: {.columns}

::: {.column width=55%"}

* 📧 ondrej.mottl(at)gmail.com
* 🦋 [ondrejmottl.bsky.social](https://bsky.app/profile/ondrejmottl.bsky.social)
* 🐱 [Github](https://github.com/OndrejMottl)
* 🆔 [ORCID](https://orcid.org/0000-0002-9796-5081)
* 🌐 [Personal webpage](https://ondrejmottl.github.io/)
:::

::: {.column width="20%"}
:::

::: {.column width="25%"}

```{r}
#| label: QR code https://bit.ly/ondrej_mottl 
qr_personal_web <-
  qrcode::qr_code(
    "https://bit.ly/ondrej_mottl",
    ecl = "H"
  )

qrcode::generate_svg(
  qrcode = qr_personal_web,
  filename = here::here("Presentation/Materials/QR/qr_personal_web.svg"),
  foreground = colours[["black"]],
  background = colours[["white"]],
  show = FALSE
)

include_local_figure("QR/qr_personal_web.svg")
```
:::

::::

## {background-image="../Presentation/Materials/R_generated/Fossil_pollen/Neotoma_spatial_data_full-2025-12-09.png" background-size="1500px" background-repeat="no-repeat" background-opacity="0.65"}

<br>
<br>
<br>

:::: {.columns}

::: {.column width = "20%"}
:::

::: {.column width = "60%" .text-center}

::: {.text-bold .r-fit-text .text-color-black}
\>6650
:::

::: {.blockquote}
fossil pollen timeseries (records)
:::


:::

::::

::: {.footer}
Fossil pollen datasets accessed from Neotoma on 2025-12-09
:::

## Palaeoecological dataset compilation

<br>

:::: {.columns}

::: {.column width = "70%"}

```{r}
#| label: compilation_1
include_local_figure("FOSSILPOL/Visualisation-compilation/compilation_1.png")
```
:::

::: {.column width = "30%"}
:::

::::

## Palaeoecological dataset compilation

<br>

:::: {.columns}

::: {.column width = "70%"}

```{r}
#| label: compilation_2
include_local_figure("FOSSILPOL/Visualisation-compilation/compilation_2.png")
```
:::

::: {.column width = "30%"}
:::

::::

## Palaeoecological dataset compilation

<br>

:::: {.columns}

::: {.column width = "70%"}

```{r}
#| label: compilation_3
include_local_figure("FOSSILPOL/Visualisation-compilation/compilation_3.png")
```
:::

::: {.column width = "30%"}
:::

::::

## Palaeoecological dataset compilation

<br>

:::: {.columns}

::: {.column width = "70%"}

```{r}
#| label: compilation_4
include_local_figure("FOSSILPOL/Visualisation-compilation/compilation_4.png")
```
:::

::: {.column width = "30%"}
:::

::::

## Palaeoecological dataset compilation

<br>

:::: {.columns}

::: {.column width = "70%"}

```{r}
#| label: compilation_5
include_local_figure("FOSSILPOL/Visualisation-compilation/compilation_5.png")
```
:::

::: {.column width = "30%"}
:::

::::


## Palaeoecological dataset compilation

<br>

:::: {.columns}

::: {.column width = "70%"}

```{r}
#| label: compilation_full
include_local_figure("FOSSILPOL/Visualisation-compilation/compilation_full.png")
```
:::

::: {.column width = "30%" .incremental}

- Macro-scale data analysis
- Project specific
- Data quality control and reproducibility

:::

::::

# 

:::: {.columns}

::: {.column width = "50%"}
```{r}
#| label: fossilpol_logo_2
include_local_figure("Logos/FOSSILPOL_logo_600ppi.png")
```
:::

::: {.column width = "50%" .center-vertical .text-larger .text-center}
The workflow to process global [palaeoecological data]{.text-highlight-purple} of fossil pollen for [vegetation]{.text-highlight-pink }-based [macroecological]{.text-highlight-coral} [synthesis]{.text-highlight-orange}
:::

::::


## [Inputs]{.text-color-white} {background-image="../Presentation/Materials/FOSSILPOL/Banners/Banner_1.png" background-size="100% 20%" background-position="top left" background-repeat="no-repeat"}

<br>

```{r}
#| label: workflow_0
#| out.height: 100%
#| out.width: NULL
include_local_figure("FOSSILPOL/Visualisation-workflow/workflow_0.png")
```

## [SOURCING]{.text-color-white} {background-image="../Presentation/Materials/FOSSILPOL/Banners/Banner_2.png" background-size="100% 20%" background-position="top left" background-repeat="no-repeat"}

<br>

```{r}
#| label: workflow_2
#| out.height: 100%
#| out.width: NULL
include_local_figure("FOSSILPOL/Visualisation-workflow/workflow_2.png")
```

## [CHRONOLOGIES]{.text-color-white} {background-image="../Presentation/Materials/FOSSILPOL/Banners/Banner_3.png" background-size="100% 20%" background-position="top left" background-repeat="no-repeat"}

<br>

```{r}
#| label: workflow_4
#| out.height: 100%
#| out.width: NULL
include_local_figure("FOSSILPOL/Visualisation-workflow/workflow_4.png")
```

## [HARMONISATION]{.text-color-white} {background-image="../Presentation/Materials/FOSSILPOL/Banners/Banner_4.png" background-size="100% 20%" background-position="top left" background-repeat="no-repeat"}

<br>

```{r}
#| label: workflow_6
#| out.height: 100%
#| out.width: NULL
include_local_figure("FOSSILPOL/Visualisation-workflow/workflow_6.png")
```

## [FILTERING]{.text-color-white} {background-image="../Presentation/Materials/FOSSILPOL/Banners/Banner_5.png" background-size="100% 20%" background-position="top left" background-repeat="no-repeat"}

<br>

```{r}
#| label: workflow_8
#| out.height: 100%
#| out.width: NULL
include_local_figure("FOSSILPOL/Visualisation-workflow/workflow_8.png")
```

## [Outputs]{.text-color-white} {background-image="../Presentation/Materials/FOSSILPOL/Banners/Banner_6.png" background-size="100% 20%" background-position="top left" background-repeat="no-repeat"}

<br>

```{r}
#| label: workflow_full
#| out.height: 100%
#| out.width: NULL
include_local_figure("FOSSILPOL/Visualisation-workflow/workflow_full.png")
```

## Documentation

### Website

<br>

:::: {.columns}

::: {.column width="40%"}

```{r}
#| label: website_preview
include_local_figure("Printscreens/website_preview.png")
```
:::

::: {.column width="60%" .fragment}

```{r}
#| label: website_doc_preview
include_local_figure("Printscreens/website_doc_preview.png")
```

[check it out!]{.text-highlight-orange} - [bit.ly/FOSSILPOL](https://bit.ly/FOSSILPOL)

:::

::::

::: {.text-center .fragment}

Now billingual: [English]{.text-highlight-purple} and [Spanish]{.text-highlight-pink}

:::


## FOSSILPOL

:::: {.columns}

::: {.column width="75%" .incremental}

<br>

- Handles all the steps and flags places where the [user]{.text-highlight-purple} needs to specify their [choices]{.text-highlight-pink}
- Modular structure to allow [flexibility]{.text-highlight-coral} and [customisation]{.text-highlight-orange} for different [projects]{.text-highlight-yellow}
- Open-source and fully [reproducible]{.text-highlight-green} workflow written in [R]{.text-highlight-blue}
:::

::: {.column width="25%" .fragment}

<br> 

```{r}
#| label: QR code https://bit.ly/FOSSILPOL 
qr_fossilpol <-
  qrcode::qr_code(
    "https://bit.ly/FOSSILPOL",
    ecl = "H"
  )

qrcode::generate_svg(
  qrcode = qr_fossilpol,
  filename = here::here("Presentation/Materials/QR/qr_fossilpol.svg"),
  foreground = colours[["black"]],
  background = colours[["white"]],
  show = FALSE
)

include_local_figure("QR/qr_fossilpol.svg")
```
:::

::::

:::: {.columns .fragment}

::: {.column width="60%" .text-center}
'*A guide to the processing and standardisation of global palaeoecological data for large-scale syntheses using fossil pollen*' (GEB 2023)

[![](https://img.shields.io/badge/DOI-10.1111%2Fgeb.13693-yellow)](https://doi.org/10.1111/geb.13693)
:::

::: {.column width="5%"}
:::

::: {.column width="35%"}

```{r}
#| label: gep_certificate
include_local_figure("Printscreens/GEB_certifiate.png")
```


:::

::::


